Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-07-01 paper/src/5_evaluation.tex
modify 5

In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region.%, using
Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, we compare I/O througput and overall cost between direct I/O and I/O burst buffer with different cache hit rate, here cache hit rate means the percentage of data in total I/O is buffered in buffer queue or the percentage of data can write to buffer queue before queue becomes full.
since when we use I/O burst buffer, read and write throughput are the same, both is equal to throughput between computing nodes and I/O nodes, for using I/O burst buffer, we use this throughput value.
%m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
%m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}. Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
%According to these data and definition described above, we use values defined below.

@@

First we compare the I/O throughput between direct connection and I/O burst buffer (both cache miss and cache hit) on TSUBAME and Amazon EC2.
In this simulation we assume that both I/O buffer nodes and computing nodes use m3.xlarge instance and Amazon Linux AMI, and the number of I/O buffer nodes is equal to number of computing nodes in order to achieve a maximum Ethernet throughput.
In practice, I/O buffer nodes may have a better Ethernet condition than computing nodes, but there also will be many users running their application on large amount of computing nodes, so there can be several computing nodes reading data from or writing data to one I/O nodes, Ethernet bandwidth also can be fully utilized.

Fig.~\ref{throughput comparison} and Fig.~\ref{throughput cache rate} shows the throughput comparison with and without I/O burst buffer.
For without I/O burst buffer, each computing nodes will read from and write data to storage directly and concurrently, when number of nodes is small, throughput increases as number of nodes increses, but after throughput reach the Internet throughput(number of nodes equals to 10 in our case), throughput becomes stable, means Internet bandwidth is fully utilized, and since that I/O is limited by Internet bandwidth.

@@

The large difference shows in cache hit 100\%(Fig.~\ref{throughput cache rate}), since all required files are buffered in buffer queue, also buffer queue is not full, computing nodes can read from and write to buffer queue every time.
As we mentioned, Ethernet throughput in Amazon EC2 shows a strong scalablity, I/O throughput can finially achieve around 2700MB/s, about 20 times faster than direct I/O and also 0\%cache hit cases.

@@

%If file is buffered in I/O buffer nodes, computing nodes can read it through Ethernet, Fig.~\ref{cache hit}, shows the comparison, we can see that when Ethernet throughput larger than Internet throughput, our solution can achieve a higher I/O throughput, here we assume that Ethernet throuhput can be lower than Internet throughput, but from Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{throughput TSUBAME}, Ethernet usually is faster than Internet, and by using our solution can achieve a high throughput.

@@

Then we compare overall cost with and without I/O burst buffer, As we mentioned, cost will be determined by both number of nodes and execution time, 
As we showed, By using I/O burst buffer, we can achieve a high I/o throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
\[cost=\frac{Data~size}{throughput}\times cost\times node\]
According to Amazon pricing policy, m3.xlarge instance is charged \$0.405 for each hour usage in Asia Pacific(Tokyo).
For direct I/O, nodes is equal to number of computing nodes, but for I/O burst buffer, since we assume that number of I/O nodes is equal to number of computing nodes, here the value of node in above formular will be 2 times number of computing nodes.

>>>>

In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region.%, using
Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, we compare I/O throughput and overall cost between direct I/O and I/O burst buffer with different cache hit rate, here cache hit rate means the percentage of data in total I/O is buffered in buffer queue or the percentage of data can write to buffer queue before queue becomes full.
since when we use I/O burst buffer, read and write throughput are the same, both are equal to throughput between computing nodes and I/O nodes,  we use this throughput value for I/O throughput when use I/O burst buffer..
%m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
%m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}. Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
%According to these data and definition described above, we use values defined below.

@@

First we compare the I/O throughput between direct connection and I/O burst buffer with different cache hit rate on TSUBAME and Amazon EC2.
In this simulation we assume that both I/O buffer nodes and computing nodes use m3.xlarge instance and Amazon Linux AMI, and the number of I/O buffer nodes is equal to number of computing nodes in order to achieve a maximum Ethernet throughput.
In practice, I/O buffer nodes may have a better Ethernet condition than computing nodes, but there also will be many users running their application on large amount of computing nodes, so there can be several computing nodes reading data from or writing data to one I/O nodes, Ethernet bandwidth also can be fully utilized.

Fig.~\ref{throughput comparison} and Fig.~\ref{throughput cache rate} shows the throughput comparison with and without I/O burst buffer.
For direct I/O, each computing nodes will read from and write data to storage directly and concurrently, when number of nodes is small, throughput increases as number of nodes increses, but after throughput reach the Internet bandwidth( 120MB/s when number of nodes equals to 10 in our case), throughput becomes stable, means Internet bandwidth is fully utilized, and since that I/O is limited by Internet bandwidth.

@@

The large difference shows in cache hit 100\%(Fig.~\ref{throughput cache rate}), since all required files are buffered in buffer queue, also buffer queue is not full, computing nodes can read from and write to buffer queue each time.
As we mentioned, Ethernet throughput in Amazon EC2 shows a strong scalablity, I/O throughput can finially achieve around 2700MB/s, about 20 times faster than direct I/O and also 0\%cache hit cases.

@@

In this simulation we only consider one job use up to 20 computing nodes, but in practice, large number of computing nodes issue read and write request concurrently, Fig.~\ref{maximum throughput} shows the maximum throughput of different cache hit rate and direct I/O, we can see that although reading can not achieve a cache hit rate, until buffer queue is full, writing can achieve a extremely high throughput.
%If file is buffered in I/O buffer nodes, computing nodes can read it through Ethernet, Fig.~\ref{cache hit}, shows the comparison, we can see that when Ethernet throughput larger than Internet throughput, our solution can achieve a higher I/O throughput, here we assume that Ethernet throuhput can be lower than Internet throughput, but from Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{throughput TSUBAME}, Ethernet usually is faster than Internet, and by using our solution can achieve a high throughput.

@@

Then we compare overall cost with and without I/O burst buffer, As we mentioned, cost will be determined by both number of nodes and execution time. 
As we showed, By using I/O burst buffer, we can achieve a high I/O throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
\[cost=\frac{Data~size}{throughput}\times cost\_per\_hour\times node\]
According to Amazon pricing policy, m3.xlarge instance is charged \$0.405 for each hour usage in Asia Pacific(Tokyo).
For direct I/O, nodes is equal to number of computing nodes, but for I/O burst buffer, since we assume that number of I/O nodes is equal to number of computing nodes, here the value of node in above formular will be 2 times number of computing nodes.
